\documentclass[10pt,a4paper,utf8]{article}

\usepackage[a4paper,inner=100pt,outer=100pt,textheight=630pt,centering]{geometry}

\usepackage{enumerate}
\usepackage[usenames,dvipsnames]{xcolor}
\usepackage[pagebackref,citecolor=blue,linkcolor=OliveGreen,urlcolor=Mahogany,colorlinks]{hyperref}
\usepackage[utf8]{inputenc}
\usepackage{color}
\usepackage{url}
\usepackage{amssymb}
\usepackage{amsmath}
\usepackage{amsthm}
\usepackage{cases}
\usepackage[innertopmargin=-5,skipbelow=-5]{mdframed}
\usepackage{stmaryrd}
\usepackage{mathpartir}
\usepackage{tikz}
\usepackage{tikz-cd}
\usetikzlibrary{arrows,matrix,decorations.pathmorphing,
  decorations.markings, calc, backgrounds}

\theoremstyle{plain}
\newtheorem{theorem}{Theorem}
\newtheorem*{theorem*}{Theorem}
\newtheorem{lemma}[theorem]{Lemma}
\newtheorem*{lemma*}{Lemma}
\newtheorem{corollary}[theorem]{Corollary}
\newtheorem*{corollary*}{Corollary}
\newtheorem{proposition}[theorem]{Proposition}
\newtheorem*{proposition*}{Proposition}

\theoremstyle{definition}
\newtheorem{definition}[theorem]{Definition}
\newtheorem*{definition*}{Definition}
\newtheorem{example}[theorem]{Example}
\newtheorem*{example*}{Example}

\theoremstyle{remark}
\newtheorem{remark}[theorem]{Remark}
\newtheorem*{remark*}{Remark}

\input{macro}

\begin{document}

\title{Cubical Type Theory: a constructive interpretation of the
  univalence axiom\footnote{This material is based upon work supported
    by the National Science Foundation under agreement
    No. DMS-1128155. Any opinions, findings and conclusions or
    recommendations expressed in this material are those of the
    author(s) and do not necessarily reflect the views of the National
    Science Foundation.}}

\author{Cyril Cohen, Thierry Coquand, Simon Huber, and Anders Mörtberg}

\date{}

\maketitle

\begin{abstract}
  This paper presents a type theory in which it is possible to
  directly manipulate $n$-dimensional cubes (points, lines, squares,
  cubes, etc.) based on an interpretation of dependent type theory in
  a cubical set model. This enables new ways to reason about identity
  types, for instance, function extensionality is directly provable in
  the system. Further, Voevodsky's univalence axiom is provable in
  this system. We also explain an extension with some higher inductive
  types like the circle and propositional truncation. Finally we
  provide semantics for this cubical type theory in a constructive
  meta-theory.
\end{abstract}

\tableofcontents

\input{cubicaltt}

\subparagraph*{Acknowledgements}

This work originates from discussions between the four authors around an implementation
of a type system corresponding to the model described in~\cite{BCH}. This implementation
indicated a problem with the representation of higher inductive types, e.g., the elimination rule
for the circle, and suggested the need of extending this cubical model with a diagonal 
operation. The general framework (uniformity condition, connections, semantics of spheres and propositional 
truncation) is due to the second author. In particular, the glueing operation with its composition was 
introduced as a generalization of the operation described in~\cite{BCH} transforming an equivalence
into a path, and with the condition $A = \Glue~[]~A$. In a first attempt, we tried to force ``regularity'', 
i.e., the equation $\transport~i~A~a_0 = a_0$ if $A$ is independent of $i$ (which seemed to be necessary
in  order to get filling from compositions, and which implies $\Path = \Id$).
There was a problem however for getting regularity for the universe, that was discovered by Dan Licata (from 
discussions with Carlo Angiuli and Bob Harper). Thanks to this discovery, it was realized that 
regularity is actually not needed for the model to work. In particular, the second author
adapted the definition of filling from composition as in Section \ref{sec:kan-filling},
the third author noticed that we can remove the condition $A = \Glue~[]~A$, and together with the last author,
they derived the univalence axiom from the glueing operation as presented in the appendix.
This was surprising since glueing was introduced
a priori only as a way to transform equivalences into paths, but was later explained by a remark of Dan Licata
(also presented in the appendix: we get univalence as soon as the transport map associated to this
path is path equal to the given equivalence). 
The second author introduced then the restriction operation $\Gamma,\varphi$
on contexts, which, as noticed by Christian Sattler, can be seen as an explicit syntax for the notion of 
cofibration, and designed the other proof of univalence in \sect{sec:univalence-axiom} from
discussions between Nicola Gambino, Peter LeFanu Lumsdaine and the third author. Not having regularity, the type of 
paths is not the same as the $\Id$ type but, as explained in \sect{sec:identitytypes}, we can recover
the usual identity type from the path type, following an idea of Andrew Swan.

\medskip

The authors would like to thank the referees and Mart\'in Escard\'o, Georges Gonthier,
Dan Grayson, Peter Hancock, Dan Licata, Peter LeFanu Lumsdaine,
Christian Sattler, Andrew Swan, Vladimir Voevodsky for many
interesting discussions and remarks.

\bibliographystyle{plainurl}% the recommended bibstyle
\bibliography{references}

\newpage

\appendix
\input{appendix}

\end{document}

%% Local Variables:
%% ispell-local-dictionary: "english"
%% mode: latex flyspell
%% TeX-master: "main"
%% End:
